% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2014 Ethan House <ewhhouse@gmail.com> http://ehouse.io
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
%\usepackage{fullpage}
%\usepackage{shading}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
%\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Ethan House}  & (Cell) 610-800-5036\\
231 Golden Rod Lane &  ewhhouse@gmail.com \\
Rochester, NY 14623 & http://blog.ehouse.io\\
& http://github.com/ehouse\\
%& http://linkedin.com/in/ethanwhouse\\
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{Rochester Institute of Technology}{Expected Graduation 2016}{BS Applied Networking and Systems Administration}{}
	%\begin{itemize}
		%\resitem{Relevant courses: Semiconductor Devices: Physics and Modelling, Digital VLSI Design, Amorphous Silicon, Mixed-signal modelling with VHDL-AMS}
	%\end{itemize}

\end{itemize}

\resheading{Work Experience}
\begin{itemize}
	\item
	\ressubheading{Research Computing}{Rochester, NY}{SysAdmin}{August 2014 -}
	\begin{itemize}
		\resitem{Created open source system to distribute rsync loads evenly to maximize limited system resources.}
	\end{itemize}
	\item	
	\ressubheading{Exablox}{Sunnyvale, CA}{DevOps}{June 2013 - Jan 2014}
	\begin{itemize}	
		\resitem{Implemented security standards with password restrictions, LDAP, and AWS IAM roles.}
		\resitem{Maintained AWS infrastructure(EC2, S3, R53) and setup Nagios/Icinga, DNS, KVM/QEMU and Cloud Formation}
	\end{itemize}
	\item
	\ressubheading{RIT Data Center}{Rochester, NY}{Data Center Operator}{Jan 2013 - Sep 2014}
	\begin{itemize}
		\resitem{Monitor and operate Data Center systems such as UC4, Networker, and PeopleSoft Services.}
	\end{itemize}
	
	\item
	\ressubheading{Navy SEAP/NRIEP Internship}{Philadelphia, PA}{Lead Developer}{Summer 2011,2012}
	\begin{itemize}
		\resitem{Project leader in developing framework to allow easy creation of 3D training simulations using Kinect and in house built tracking hardware. }
		\resitem{Required Secret Clearance.}
	\end{itemize}

\end{itemize}

\resheading{Skills}

\begin{description}
\item[Languages:]
Python, Perl, Bash, C/C++, PHP
\item[Operating Systems:]
Linux (Red Hat, Debian), FreeBSD, OpenBSD, Cisco IOS
\item[Applications:]Puppet, Ansible, Fabric, PF 
\item[Services:]MySQL, PostgreSQL, BIND, LDAP, Kerberos, Mail(postfix, dovecot), Web(Apache,Nginx, Nagios/Icinga), 
\end{description}

\resheading{Interests}

\begin{description}
\item[Volunteer EMT:]Trainee EMT for Pittsford Volunteer Ambulance. 
\item[Computer Science House:] Member and SysAdmin for student run organization based around extra curricular learning. Maintained network infrastructure, DNS, NFS, Mail for 100+ members. 
\item[Coding:] Active in open source communities with projects on Github. 
\item[Martial Arts:] 2nd degree black belt in Karate and taught students for several years.

\end{description}

\end{document}